### 2017-08-17 doc/MSc-dissertation.tex
results prm>1

\usepackage{graphics}
\usepackage{listings}
\usepackage{fullpage,epsf,graphicx, amstext,url,bm,amsmath, amssymb, caption}

@@

\subsection{$Re_M^{crit}$ for $Pr_M=1$}

@@

Doing a series of simulations with unity magnetic Prandtl number with varying magnetic diffusivity within the range $\eta=[0.01-1.75]$ up to code-time $100$ the onset of dynamo action was observed between $\eta=0.015$ and $\eta=0.0175$. The total magnetic energy in time can be seen in fig.~\ref{fig5.12}, which corresponds to runs S0 to S3 in table~\ref{tableB1}. The relation between the maximum wave number and the Kolmogorov microscales $k_{max}/k_\nu$ and $k_{max}/k_\eta$ is helpful to know how well resolved a given simulation is. Particularly, and as it was mentioned in section~\ref{sec4.2}, when $k_{max}/max(k_\nu, k_\eta) \geq 1.25$ then the simulation is said to be fully resolved, whereas if $1 < k_{max}/max(k_\nu, k_\eta) < 1.25$ a partially resolved similation, and if $k_{max}/max(k_\nu, k_\eta) \leq 1$ the simulation is under resolved. Having said this, it is noted that in table~\ref{tableB1} two simulations for the S-runs are partially resolved that correspond to $\eta=0.015$ and $\eta=0.0175$, and the same is true for the L-runs.

\begin{figure}[!ht]
\centering
\includegraphics[width=0.7\textwidth]{{img/prm1/ss_prm_1_short}.png}
\caption{Temporal evolution of the total magnetic energy for simulations with ${Pr_M=1}$ from $t=60$ to $t=100$.}
\label{fig5.12}
\end{figure}

@@

The range of magnetic Prandtl number was then broadened and it was seen that this critical value of magnetic Reynolds number depends on $Pr_M$. The first thing that was necessary to study the onset of small-scale dynamo action was to define a way to determine weather there was dynamo action or not in a specific simulation.

For simulations with $Pr_M$ larger than unity it was possible to identify a critical magnetic Reynolds number $Re_M$. After doing this it was possible to obtain a critical magnetic Prandtl number for which dynamo action is shut down. This qualitatively agrees with the results shown in~\cite{schekochihin2004critical}.

@@

\section{Discussion of your results}

@@

\begin{table}[h]
\begin{center}
\begin{tabular}{||c|c|c|c|c|c|c|c||}
\hline
\textbf{Run} & $ \bm{\eta} $ & $ \bm{ Pr_M} $ & $ \bm{ Re} $ & $ \bm{ Re_M} $ & $ \bm{ \frac{k_{max}}{k_\nu}} $ & $ \bm{ \frac{k_{max}}{k_\eta}} $ & $ \bm{ \langle E_M^{ss}} \rangle $ \\ \hline \hline
S0 & 0.01 & 1 & $ 69 \pm 6 $ & $ 69 \pm 6 $ & $ 2.33911 $ & $ 2.33911 $ & $ 0.022 \pm 0.003 $ \\ \hline
S1 & 0.0125 & 1 & $ 55 \pm 4 $ & $ 68 \pm 5 $ & $ 2.77289 $ & $ 2.34558 $ & $ 0.014 \pm 0.001 $ \\ \hline
S2 & 0.015 & 1 & $ 43 \pm 3 $ & $ 64 \pm 5 $ & $ 1.5311 $ & $ 1.12962 $ & $ 0.005 \pm 0.001 $ \\ \hline
S3 & 0.0175 & 1 & $ 37 \pm 2 $ & $ 65 \pm 3 $ & $ 1.69408 $ & $ 1.11341 $ & $ 0.001 \pm 0.000 $ \\ \hline \hline
L0 & 0.01 & 1 & $ 69 \pm 4 $ & $ 69 \pm 4 $ & $ 2.30562 $ & $ 2.30562 $ & $ 0.023 \pm 0.004 $ \\ \hline
L1 & 0.0125 & 1 & $ 56 \pm 4 $ & $ 70 \pm 4 $ & $ 2.70774 $ & $ 2.29048 $ & $ 0.007 \pm 0.003 $ \\ \hline
L2 & 0.015 & 1 & $ 46 \pm 4 $ & $ 69 \pm 6 $ & $ 1.52046 $ & $ 1.12177 $ & $ 0.000 \pm 0.000 $ \\ \hline
L3 & 0.0175 & 1 & $ 39 \pm 3 $ & $ 69 \pm 6 $ & $ 1.70577 $ & $ 1.1211 $ & $ 0.000 \pm 0.000 $ \\ \hline
\end{tabular}
\end{center}
\caption{Runs for the onset of dynamo action in the $Pr_M=1$ case. The S-runs are only from code time 0 to 100, while the L-runs are (at least) from code time 0 to 300.}
\label{tableB1}
\end{table}

>>>>

\usepackage{graphics}
\usepackage{listings}
\usepackage{fullpage,epsf,graphicx, amstext,url,bm,amsmath, amssymb, caption, longtable}

@@

\subsection{$Re_M^{crit}$ for $Pr_M=1$}
\label{subsec5.3.1}

@@

Doing a series of simulations with unity magnetic Prandtl number with varying magnetic diffusivity within the range $\eta=[0.01-0.02]$ up to code-time $100$ the onset of dynamo action was observed between $\eta=0.02$ and $\eta=0.0175$. The total magnetic energy in time can be seen in fig.~\ref{fig5.12}, which corresponds to runs S0 to S4 in table~\ref{tableB1}. From these simulations it is concluded that the critical magnetic Reynolds number lies somewhere in the range $Re_M^{crit}=[31:39]$, where $Re_M=u_{rms}L/\eta$ and $L$ is the kinetic integral scale given by the eDNS2017 code.

The relation between the maximum wave number and the Kolmogorov microscales $k_{max}/k_\nu$ and $k_{max}/k_\eta$ is helpful to know how well resolved a given simulation is. Particularly, and as it was mentioned in section~\ref{sec4.2}, when $k_{max}/max(k_\nu, k_\eta) \geq 1.25$ then the simulation is said to be fully resolved, whereas if $1 < k_{max}/max(k_\nu, k_\eta) < 1.25$ a partially resolved simulation, and if $k_{max}/max(k_\nu, k_\eta) \leq 1$ the simulation is under resolved. Having said this, it is noted that in table~\ref{tableB1} all simulations for the S-runs (short) are fully resolved.

\begin{figure}[!ht]
\centering
\includegraphics[width=0.7\textwidth]{{img/prm1/ss_prm_1_short}.png}
\caption{Temporal evolution of the total magnetic energy for simulations with ${Pr_M=1}$ from $t=60$ to $t=100$. These correspond to the S-runs in table~\ref{tableB1}.}
\label{fig5.12}
\end{figure}

\begin{figure}[!ht]
\centering
\includegraphics[width=0.7\textwidth]{{img/prm1/ss_prm_1_long}.png}
\caption{Temporal evolution of the total magnetic energy for simulations with ${Pr_M=1}$ from $t=60$ to $t=300$. These correspond to the L-runs in table~\ref{tableB1}.}
\label{fig5.13}
\end{figure}

Driven by the substantial difference between the total magnetic energy of S1 and S2/3, and because of doubts regarding having reached a real steady state in figure~\ref{fig5.12}, a set of runs with longer times was performed. This second set of simulations was done up to (at least) code time 300, but only for the magnetic diffusivity range $\eta=[0.01:0.0175]$. These simulations correspond to the L-runs (long) of table~\ref{tableB1}, and are plotted in the code time range 60 to 300 and shown in fig.~\ref{fig5.13}. It is clear that a transition from no dynamo action to dynamo action occurs somewhere between $\eta=0.015$ and $\eta=0.0125$. As a result, it is now possible to state that the critical magnetic Reynolds number lays somewhere in the range $Re_M^{crit}=[42:60]$. This is consistent with values found in the literature~\cite{brandenburg2005astrophysical, kazantsev1968enhancement}. A quick check of the L-runs in table~\ref{tableB1} shows that all the simulations used for fig.~\ref{fig5.13} are also fully resolved.

\subsection{Dynamo onset map}

After obtaining an estimate for the magnetic Reynolds number for unity $Pr_M$, and motivated in~\cite{schekochihin2004critical}'s discussion of the dependence of $Re_M^{crit}$ with $Re$, a larger set of runs was performed. The aim of this set of runs was to check what happened with the total magnetic energy at ``infinity'' through ensemble averages for values of $\nu$, that showed no dynamo action in the $Pr_M=1$ case, by varying the magnetic Prandtl number below and above unity. These simulations correspond to M-runs in table~\ref{tableB2}. There it can be checked that all simulations are appropriately resolved since for all simulations $min(k_{max}/k_\nu, k_{max}/k_\eta) > 1.25$.

\begin{figure}[!ht]
\centering
\includegraphics[width=0.9\textwidth]{{img/map/3d_ss}.png}
\caption{Ensemble average of the total magnetic energy from $t=90$ to $t=100$ ($dt=0.1$) for all simulations in table~\ref{tableB2}.}
\label{fig5.14}
\end{figure}

Using the information of table~\ref{tableB2} a heat map was generated that shows the temporal average of the total magnetic energy in the range 60 to 100 of code time, every 0.1 units of code time, fig.~\ref{fig5.14}, where it is clear that for the higher values of magnetic diffusivity dynamo action cannot be sustained. This is a result of the magnetic field not being turbulent enough, i.e. the magnetic Reynolds number is too small. A heat map for the magnetic Reynolds number can be generated in a similar way than for $\langle E_M(t\rightarrow\infty) \rangle$, and it is shown in fig.~\ref{fig5.15}.

\begin{figure}[!ht]
\centering
\includegraphics[width=0.9\textwidth]{{img/map/3d_ss_Rm}.png}
\caption{Magnetic Reynolds number for all simulations in table~\ref{tableB2}.}
\label{fig5.15}
\end{figure}

There is an obvious resemblance between fig.~\ref{fig5.14} and~\ref{fig5.15} because the dark parts of the $\langle E_M \rangle$ heat map, which did not achieve dynamo action, have magnetic Reynolds number smaller than $Re_M^{crit}(=[42:60]$ for $Pr_M=1)$. The shape of fig.~\ref{fig5.15} is not surprising at all since the magnetic Reynolds number is inversely proportional to $\eta$ ($Re_M=u_{rms}L/\eta$), so by decreasing the magnetic diffusivity the $Re_M$ increases.

Regarding fig.~\ref{fig5.14}, an interesting feature of the simulations that appear to have dynamo action when $Pr_M \sim 1$ ($\nu=[0.01, 0.0125, 0.015]$) is that no dynamo action is sustained when the magnetic Prandtl number is $Pr_M=0.2$. However, since in subsection~\ref{subsec5.3.1} it was seen that the simulations for $\eta=0.015\text{ and }0.0175$ did not reach a steady state after 100 units of code time, it is important to extend some of the simulations that appear to have dynamo action to longer times such that they reach a steady state and it is possible to confirm whether or not they sustain dynamo action.

The first thing that was done was generate two sets of longer runs to check what happens with the apparent dynamo action for $\eta=0.0125\text{ and }0.015$. These runs correspond to table~\ref{tableB3} and the total magnetic energy for different magnetic Prandtl numbers are shown in figs.~\ref{fig5.16} and~\ref{fig5.17} for $\nu=0.0125$ and $\nu=0.015$ respectively. The simulations with $\eta=0.0125, Pr_M=0.6$ and $\eta=0.015, Pr_M=1.2$ were run until $t=600$, and by that time both of them had completely lost their total magnetic energy due to dissipation. This leads to the statement that simulations with $\eta \geq 0.015$ cannot sustain dynamo action, and the largest magnetic Reynolds number of a simulation with $\eta=0.015$ is $Re_M=47\pm4$.

\begin{figure}[!ht]
\centering
\begin{minipage}{.5\textwidth}
  \centering
  \captionsetup{justification=centering}
  \includegraphics[width=0.95\linewidth]{{img/map/long/ss_eta_0.0125}.png}
  \caption{Time evolution of the total magnetic energy for $\eta=0.0125$ and $Pr_M=[0.6, 0.8, 1, 1.2]$.}
  \label{fig5.16}
\end{minipage}%
\begin{minipage}{.5\textwidth}
  \centering
  \captionsetup{justification=centering}
  \includegraphics[width=0.95\linewidth]{{img/map/long/ss_eta_0.015}.png}
  \caption{Time evolution of the total magnetic energy for $\eta=0.015$ and $Pr_M=[0.8, 1, 1.2]$.}
  \label{fig5.17}
\end{minipage}
\end{figure}

Regarding the $\eta=0.0125$ simulation, which is the largest magnetic diffusivity that is able to sustain dynamo action that was worked with, it is interesting to note that a small enough magnetic Prandtl number, large enough Reynolds number, is able to shut down dynamo action. Furthermore, it is possible to state that the critical magnetic Reynolds number for $Pr_M < 1$ in this case is somewhere in the range $Re_M^{crit}=[50:59]$.

@@

After seeing that decreasing the magnetic Prandtl number to values below unity was detrimental for dynamo action, and remembering the inverse duality observed in the two dimensional field slices in fig.~\ref{fig5.1}, larger values of $Pr_M > 1$ became of interest. It is well known that there exists a duality between the kinetic and the magnetic fields. As a matter of fact, a set of variables called the Els\"asser variables, which are defined by eqn.~\ref{eq5.2}, are commonly used in the description of MHD because of the especially simple form the MHD equations take with these~\cite{tobias2011mhd, biskamp1997nonlinear}. Due to this duality of the fields, it would be expected that, for a fixed $\eta$, increasing $Pr_M$ above unity would give a critical value that kills dynamo action, just like decreasing $Pr_M$ below unity does.

\begin{align}
 \bm z^{\pm} = \bm u \pm \bm b \label{eq5.2}
\end{align}

With this in mind, the range of magnetic Prandtl number was then broadened and it was seen that the critical value of magnetic Reynolds number needed to sustain dynamo action depends on $Pr_M$, which is part of the central argument of~\cite{schekochihin2004critical, schekochihin2005onset}. Namely, they state that a rough velocity field can affect the critical magnetic Reynolds number by increasing it substantially when compared with a system with the same magnetic diffusivity, but more laminar velocity field (higher $Pr_M$).

For simulations with $Pr_M$ larger than unity it was possible to identify a critical magnetic Reynolds number $Re_M^{crit}$. For the $\eta=0.0125$ case, it is clear that $Pr_M=1.2$ is not large enough to shut down dynamo action (fig.~\ref{fig5.16}). As a result, various simulations with $\eta=0.0125$, but $Pr_M=[4, 6,\text{ and }8]$, were generated (ML0-ML2 in table~\ref{tableB3}). Then, $E_M(t)$ is shown in fig.~\ref{fig5.18} for the range $t=[60:600]$, and it is concluded that the, higher than unity, critical magnetic Prandtl number for $\eta=0.0125$ lies somewhere between $Pr_M^{crit}=[6:8]$. Comparing the magnetic Reynolds numbers of these simulations, along with their respective errors, $Re_M^{crit}$ is found to be somewhere in the range $Re_M^{crit}=[39:50]$. Recalling that for the $Pr_M < 1$ case with the same value of $\eta=0.0125$, the critical magnetic Reynolds number was $Re_M^{crit}=[50:59]$. Therefore, it looks like  ~\cite{schekochihin2004critical}.

\begin{figure}[!ht]
\centering
\includegraphics[width=0.7\textwidth]{{img/map/long/ss_eta_0.0125_4-6-8}.png}
  \caption{Time evolution of the total magnetic energy for $\eta=0.0125$ and ${Pr_M=[4, 6, 8]}$ in the range $t=[60:600]$.}
\label{fig5.18}
\end{figure}

@@

\section{Discussion}

@@

\begin{table}[h]
\begin{center}
\begin{tabular}{||c|c|c|c|c|c|c|c||}
\hline
\textbf{Run} & $ \bm{\eta} $ & $ \bm{ Pr_M} $ & $ \bm{ Re} $ & $ \bm{ Re_M} $ & $ \bm{ \frac{k_{max}}{k_\nu}} $ & $ \bm{ \frac{k_{max}}{k_\eta}} $ & $ \bm{ \langle E_M^{ss}} \rangle $ \\ \hline
S0 & 0.01 & 1 & $ 69 \pm 6 $ & $ 69 \pm 6 $ & $ 2.33911 $ & $ 2.33911 $ & $ 0.022 \pm 0.003 $ \\ \hline
S1 & 0.0125 & 1 & $ 55 \pm 4 $ & $ 55 \pm 4 $ & $ 2.77289 $ & $ 2.77289 $ & $ 0.014 \pm 0.001 $ \\ \hline
S2 & 0.015 & 1 & $ 43 \pm 3 $ & $ 43 \pm 3 $ & $ 1.5311 $ & $ 1.5311 $ & $ 0.005 \pm 0.001 $ \\ \hline
S3 & 0.0175 & 1 & $ 37 \pm 2 $ & $ 37 \pm 2 $ & $ 1.69408 $ & $ 1.69408 $ & $ 0.001 \pm 0.000 $ \\ \hline
S4 & 0.02 & 1 & $ 33 \pm 2 $ & $ 33 \pm 2 $ & $ 1.93261 $ & $ 1.93261 $ & $ 0.000 \pm 0.000 $ \\ \hline \hline
L0 & 0.01 & 1 & $ 69 \pm 4 $ & $ 69 \pm 4 $ & $ 2.30562 $ & $ 2.30562 $ & $ 0.023 \pm 0.004 $ \\ \hline
L1 & 0.0125 & 1 & $ 56 \pm 4 $ & $ 56 \pm 4 $ & $ 2.70774 $ & $ 2.70774 $ & $ 0.007 \pm 0.003 $ \\ \hline
L2 & 0.015 & 1 & $ 46 \pm 4 $ & $ 46 \pm 4 $ & $ 1.52046 $ & $ 1.52046 $ & $ 0.000 \pm 0.000 $ \\ \hline
L3 & 0.0175 & 1 & $ 39 \pm 3 $ & $ 39 \pm 3 $ & $ 1.70577 $ & $ 1.70577 $ & $ 0.000 \pm 0.000 $ \\ \hline
\end{tabular}
\end{center}
\caption{Runs for the onset of dynamo action in the $Pr_M=1$ case. The S-runs are only from code time 0 to 100, while the L-runs are (at least) from code time 0 to 300.}
\label{tableB1}
\end{table}
\begin{longtable}{||c|c|c|c|c|c|c|c||}
\hline
\textbf{Run} & $ \bm{\eta} $ & $ \bm{ Pr_M} $ & $ \bm{ Re} $ & $ \bm{ Re_M} $ & $ \bm{ \frac{k_{max}}{k_\nu}} $ & $ \bm{ \frac{k_{max}}{k_\eta}} $ & $ \bm{ \langle E_M^{ss}} \rangle $ \\ \hline
M0 & 0.01 & 2.2 & $ 31 \pm 3 $ & $ 68 \pm 6 $ & $ 4.16081 $ & $ 2.30336 $ & $ 0.028 \pm 0.002 $ \\ \hline
M1 & 0.0125 & 2.2 & $ 25 \pm 2 $ & $ 54 \pm 5 $ & $ 5.04814 $ & $ 2.79457 $ & $ 0.006 \pm 0.001 $ \\ \hline
M2 & 0.015 & 2.2 & $ 19 \pm 1 $ & $ 42 \pm 3 $ & $ 2.79941 $ & $ 1.54971 $ & $ 0.002 \pm 0.000 $ \\ \hline
M3 & 0.0175 & 2.2 & $ 16 \pm 1 $ & $ 35 \pm 3 $ & $ 3.16709 $ & $ 1.75325 $ & $ 0.003 \pm 0.000 $ \\ \hline
M4 & 0.02 & 2.2 & $ 14 \pm 1 $ & $ 30 \pm 2 $ & $ 3.5067 $ & $ 1.94126 $ & $ 0.000 \pm 0.000 $ \\ \hline
M5 & 0.0225 & 2.2 & $ 12 \pm 1 $ & $ 26 \pm 2 $ & $ 3.83564 $ & $ 2.12335 $ & $ 0.000 \pm 0.000 $ \\ \hline
M6 & 0.025 & 2.2 & $ 10 \pm 1 $ & $ 23 \pm 2 $ & $ 4.16185 $ & $ 2.30393 $ & $ 0.000 \pm 0.000 $ \\ \hline
M7 & 0.0275 & 2.2 & $ 9 \pm 1 $ & $ 20 \pm 2 $ & $ 4.475 $ & $ 2.47729 $ & $ 0.000 \pm 0.000 $ \\ \hline
M8 & 0.03 & 2.2 & $ 8 \pm 1 $ & $ 18 \pm 2 $ & $ 4.77756 $ & $ 2.64477 $ & $ 0.000 \pm 0.000 $ \\ \hline
M9 & 0.01 & 2 & $ 34 \pm 3 $ & $ 69 \pm 5 $ & $ 3.85708 $ & $ 2.29344 $ & $ 0.028 \pm 0.001 $ \\ \hline
M10 & 0.0125 & 2 & $ 27 \pm 2 $ & $ 53 \pm 4 $ & $ 4.6292 $ & $ 2.75255 $ & $ 0.003 \pm 0.000 $ \\ \hline
M11 & 0.015 & 2 & $ 20 \pm 1 $ & $ 41 \pm 2 $ & $ 2.57955 $ & $ 1.53381 $ & $ 0.005 \pm 0.001 $ \\ \hline
M12 & 0.0175 & 2 & $ 18 \pm 1 $ & $ 36 \pm 3 $ & $ 2.93851 $ & $ 1.74724 $ & $ 0.001 \pm 0.000 $ \\ \hline
M13 & 0.02 & 2 & $ 15 \pm 1 $ & $ 30 \pm 2 $ & $ 3.2649 $ & $ 1.94131 $ & $ 0.001 \pm 0.000 $ \\ \hline
M14 & 0.0225 & 2 & $ 13 \pm 1 $ & $ 26 \pm 2 $ & $ 3.56702 $ & $ 2.12096 $ & $ 0.000 \pm 0.000 $ \\ \hline
M15 & 0.025 & 2 & $ 12 \pm 1 $ & $ 23 \pm 2 $ & $ 3.86557 $ & $ 2.29848 $ & $ 0.000 \pm 0.000 $ \\ \hline
M16 & 0.0275 & 2 & $ 10 \pm 1 $ & $ 21 \pm 2 $ & $ 4.16171 $ & $ 2.47456 $ & $ 0.000 \pm 0.000 $ \\ \hline
M17 & 0.03 & 2 & $ 9 \pm 1 $ & $ 18 \pm 1 $ & $ 4.44702 $ & $ 2.64422 $ & $ 0.000 \pm 0.000 $ \\ \hline
M18 & 0.01 & 1.8 & $ 38 \pm 4 $ & $ 69 \pm 6 $ & $ 3.58194 $ & $ 2.30496 $ & $ 0.014 \pm 0.001 $ \\ \hline
M19 & 0.0125 & 1.8 & $ 32 \pm 3 $ & $ 58 \pm 5 $ & $ 4.28528 $ & $ 2.75756 $ & $ 0.014 \pm 0.002 $ \\ \hline
M20 & 0.015 & 1.8 & $ 24 \pm 2 $ & $ 44 \pm 3 $ & $ 2.39864 $ & $ 1.54352 $ & $ 0.002 \pm 0.000 $ \\ \hline
M21 & 0.0175 & 1.8 & $ 20 \pm 1 $ & $ 36 \pm 2 $ & $ 2.69717 $ & $ 1.73561 $ & $ 0.000 \pm 0.000 $ \\ \hline
M22 & 0.02 & 1.8 & $ 17 \pm 1 $ & $ 31 \pm 2 $ & $ 3.00521 $ & $ 1.93384 $ & $ 0.000 \pm 0.000 $ \\ \hline
M23 & 0.0225 & 1.8 & $ 15 \pm 1 $ & $ 27 \pm 2 $ & $ 3.29136 $ & $ 2.11798 $ & $ 0.000 \pm 0.000 $ \\ \hline
M24 & 0.025 & 1.8 & $ 13 \pm 1 $ & $ 24 \pm 2 $ & $ 3.56672 $ & $ 2.29517 $ & $ 0.000 \pm 0.000 $ \\ \hline
M25 & 0.0275 & 1.8 & $ 12 \pm 1 $ & $ 21 \pm 2 $ & $ 3.83569 $ & $ 2.46825 $ & $ 0.000 \pm 0.000 $ \\ \hline
M26 & 0.03 & 1.8 & $ 11 \pm 1 $ & $ 19 \pm 2 $ & $ 4.10309 $ & $ 2.64032 $ & $ 0.000 \pm 0.000 $ \\ \hline
M27 & 0.01 & 1.6 & $ 43 \pm 3 $ & $ 69 \pm 5 $ & $ 3.29293 $ & $ 2.3147 $ & $ 0.025 \pm 0.002 $ \\ \hline
M28 & 0.0125 & 1.6 & $ 36 \pm 3 $ & $ 57 \pm 4 $ & $ 3.89601 $ & $ 2.73859 $ & $ 0.013 \pm 0.002 $ \\ \hline
M29 & 0.015 & 1.6 & $ 27 \pm 1 $ & $ 44 \pm 2 $ & $ 2.1799 $ & $ 1.53231 $ & $ 0.008 \pm 0.001 $ \\ \hline
M30 & 0.0175 & 1.6 & $ 21 \pm 1 $ & $ 34 \pm 2 $ & $ 2.47805 $ & $ 1.74189 $ & $ 0.003 \pm 0.000 $ \\ \hline
M31 & 0.02 & 1.6 & $ 20 \pm 1 $ & $ 32 \pm 2 $ & $ 2.74879 $ & $ 1.9322 $ & $ 0.000 \pm 0.000 $ \\ \hline
M32 & 0.0225 & 1.6 & $ 17 \pm 1 $ & $ 27 \pm 2 $ & $ 3.00358 $ & $ 2.11129 $ & $ 0.000 \pm 0.000 $ \\ \hline
M33 & 0.025 & 1.6 & $ 15 \pm 1 $ & $ 25 \pm 2 $ & $ 3.25022 $ & $ 2.28467 $ & $ 0.000 \pm 0.000 $ \\ \hline
M34 & 0.0275 & 1.6 & $ 14 \pm 1 $ & $ 22 \pm 2 $ & $ 3.5052 $ & $ 2.46389 $ & $ 0.000 \pm 0.000 $ \\ \hline
M35 & 0.03 & 1.6 & $ 12 \pm 1 $ & $ 20 \pm 2 $ & $ 3.74581 $ & $ 2.63303 $ & $ 0.000 \pm 0.000 $ \\ \hline
M36 & 0.01 & 1.4 & $ 48 \pm 3 $ & $ 67 \pm 5 $ & $ 2.98449 $ & $ 2.31886 $ & $ 0.026 \pm 0.001 $ \\ \hline
M37 & 0.0125 & 1.4 & $ 39 \pm 3 $ & $ 55 \pm 4 $ & $ 3.56354 $ & $ 2.76875 $ & $ 0.011 \pm 0.001 $ \\ \hline
M38 & 0.015 & 1.4 & $ 30 \pm 2 $ & $ 42 \pm 2 $ & $ 1.95532 $ & $ 1.51923 $ & $ 0.004 \pm 0.001 $ \\ \hline
M39 & 0.0175 & 1.4 & $ 27 \pm 2 $ & $ 37 \pm 2 $ & $ 2.22137 $ & $ 1.72594 $ & $ 0.002 \pm 0.001 $ \\ \hline
M40 & 0.02 & 1.4 & $ 22 \pm 1 $ & $ 31 \pm 2 $ & $ 2.41769 $ & $ 1.87846 $ & $ 0.001 \pm 0.000 $ \\ \hline
M41 & 0.0225 & 1.4 & $ 20 \pm 1 $ & $ 27 \pm 2 $ & $ 2.68632 $ & $ 2.08719 $ & $ 0.000 \pm 0.000 $ \\ \hline
M42 & 0.025 & 1.4 & $ 18 \pm 1 $ & $ 26 \pm 2 $ & $ 2.9413 $ & $ 2.2853 $ & $ 0.000 \pm 0.000 $ \\ \hline
M43 & 0.0275 & 1.4 & $ 16 \pm 1 $ & $ 23 \pm 2 $ & $ 3.15001 $ & $ 2.44746 $ & $ 0.000 \pm 0.000 $ \\ \hline
M44 & 0.03 & 1.4 & $ 15 \pm 1 $ & $ 20 \pm 2 $ & $ 3.37335 $ & $ 2.62099 $ & $ 0.000 \pm 0.000 $ \\ \hline
M45 & 0.01 & 1.2 & $ 57 \pm 5 $ & $ 68 \pm 6 $ & $ 2.65279 $ & $ 2.31376 $ & $ 0.026 \pm 0.002 $ \\ \hline
M46 & 0.0125 & 1.2 & $ 48 \pm 4 $ & $ 57 \pm 4 $ & $ 3.13341 $ & $ 2.73293 $ & $ 0.006 \pm 0.000 $ \\ \hline
M47 & 0.015 & 1.2 & $ 36 \pm 2 $ & $ 43 \pm 2 $ & $ 1.75724 $ & $ 1.53265 $ & $ 0.004 \pm 0.000 $ \\ \hline
M48 & 0.0175 & 1.2 & $ 31 \pm 2 $ & $ 37 \pm 2 $ & $ 1.98533 $ & $ 1.7316 $ & $ 0.000 \pm 0.000 $ \\ \hline
M49 & 0.02 & 1.2 & $ 27 \pm 2 $ & $ 32 \pm 2 $ & $ 2.17819 $ & $ 1.8998 $ & $ 0.000 \pm 0.000 $ \\ \hline
M50 & 0.0225 & 1.2 & $ 23 \pm 1 $ & $ 28 \pm 2 $ & $ 2.39159 $ & $ 2.08594 $ & $ 0.000 \pm 0.000 $ \\ \hline
M51 & 0.025 & 1.2 & $ 21 \pm 1 $ & $ 25 \pm 2 $ & $ 2.61559 $ & $ 2.2813 $ & $ 0.000 \pm 0.000 $ \\ \hline
M52 & 0.0275 & 1.2 & $ 19 \pm 1 $ & $ 23 \pm 2 $ & $ 2.78617 $ & $ 2.43009 $ & $ 0.000 \pm 0.000 $ \\ \hline
M53 & 0.03 & 1.2 & $ 18 \pm 1 $ & $ 21 \pm 1 $ & $ 2.99713 $ & $ 2.61408 $ & $ 0.000 \pm 0.000 $ \\ \hline
M54 & 0.01 & 1 & $ 69 \pm 6 $ & $ 69 \pm 6 $ & $ 2.33911 $ & $ 2.33911 $ & $ 0.022 \pm 0.003 $ \\ \hline
M55 & 0.0125 & 1 & $ 55 \pm 4 $ & $ 55 \pm 4 $ & $ 2.77289 $ & $ 2.77289 $ & $ 0.014 \pm 0.001 $ \\ \hline
M56 & 0.015 & 1 & $ 43 \pm 3 $ & $ 43 \pm 3 $ & $ 1.5311 $ & $ 1.5311 $ & $ 0.005 \pm 0.001 $ \\ \hline
M57 & 0.0175 & 1 & $ 37 \pm 2 $ & $ 37 \pm 2 $ & $ 1.69408 $ & $ 1.69408 $ & $ 0.001 \pm 0.000 $ \\ \hline
M58 & 0.02 & 1 & $ 33 \pm 2 $ & $ 33 \pm 2 $ & $ 1.93261 $ & $ 1.93261 $ & $ 0.000 \pm 0.000 $ \\ \hline
M59 & 0.0225 & 1 & $ 28 \pm 1 $ & $ 28 \pm 1 $ & $ 2.07697 $ & $ 2.07697 $ & $ 0.000 \pm 0.000 $ \\ \hline
M60 & 0.025 & 1 & $ 25 \pm 1 $ & $ 25 \pm 1 $ & $ 2.26018 $ & $ 2.26018 $ & $ 0.000 \pm 0.000 $ \\ \hline
M61 & 0.0275 & 1 & $ 24 \pm 2 $ & $ 24 \pm 2 $ & $ 2.41471 $ & $ 2.41471 $ & $ 0.000 \pm 0.000 $ \\ \hline
M62 & 0.03 & 1 & $ 21 \pm 1 $ & $ 21 \pm 1 $ & $ 2.60905 $ & $ 2.60905 $ & $ 0.000 \pm 0.000 $ \\ \hline
M63 & 0.01 & 0.8 & $ 91 \pm 8 $ & $ 72 \pm 6 $ & $ 1.94556 $ & $ 2.3 $ & $ 0.026 \pm 0.001 $ \\ \hline
M64 & 0.0125 & 0.8 & $ 69 \pm 6 $ & $ 55 \pm 5 $ & $ 2.27997 $ & $ 2.69533 $ & $ 0.004 \pm 0.001 $ \\ \hline
M65 & 0.015 & 0.8 & $ 55 \pm 3 $ & $ 44 \pm 2 $ & $ 1.28378 $ & $ 1.51766 $ & $ 0.004 \pm 0.001 $ \\ \hline
M66 & 0.0175 & 0.8 & $ 48 \pm 2 $ & $ 38 \pm 2 $ & $ 1.43615 $ & $ 1.69778 $ & $ 0.000 \pm 0.000 $ \\ \hline
M67 & 0.02 & 0.8 & $ 41 \pm 2 $ & $ 33 \pm 2 $ & $ 1.61077 $ & $ 1.90422 $ & $ 0.000 \pm 0.000 $ \\ \hline
M68 & 0.0225 & 0.8 & $ 37 \pm 2 $ & $ 29 \pm 2 $ & $ 1.75671 $ & $ 2.07675 $ & $ 0.000 \pm 0.000 $ \\ \hline
M69 & 0.025 & 0.8 & $ 33 \pm 2 $ & $ 26 \pm 1 $ & $ 1.91926 $ & $ 2.26891 $ & $ 0.000 \pm 0.000 $ \\ \hline
M70 & 0.0275 & 0.8 & $ 29 \pm 1 $ & $ 23 \pm 1 $ & $ 2.05779 $ & $ 2.43267 $ & $ 0.000 \pm 0.000 $ \\ \hline
M71 & 0.03 & 0.8 & $ 27 \pm 1 $ & $ 22 \pm 1 $ & $ 2.19708 $ & $ 2.59734 $ & $ 0.000 \pm 0.000 $ \\ \hline
M72 & 0.01 & 0.6 & $ 109 \pm 5 $ & $ 66 \pm 3 $ & $ 3.18002 $ & $ 4.66465 $ & $ 0.014 \pm 0.001 $ \\ \hline
M73 & 0.0125 & 0.6 & $ 90 \pm 7 $ & $ 54 \pm 4 $ & $ 1.84714 $ & $ 2.70947 $ & $ 0.002 \pm 0.000 $ \\ \hline
M74 & 0.015 & 0.6 & $ 81 \pm 8 $ & $ 49 \pm 5 $ & $ 2.1209 $ & $ 3.11106 $ & $ 0.002 \pm 0.000 $ \\ \hline
M75 & 0.0175 & 0.6 & $ 66 \pm 4 $ & $ 40 \pm 2 $ & $ 2.38061 $ & $ 3.49201 $ & $ 0.000 \pm 0.000 $ \\ \hline
M76 & 0.02 & 0.6 & $ 53 \pm 3 $ & $ 32 \pm 2 $ & $ 1.27477 $ & $ 1.86991 $ & $ 0.000 \pm 0.000 $ \\ \hline
M77 & 0.0225 & 0.6 & $ 49 \pm 2 $ & $ 29 \pm 1 $ & $ 1.40599 $ & $ 2.06237 $ & $ 0.000 \pm 0.000 $ \\ \hline
M78 & 0.025 & 0.6 & $ 41 \pm 2 $ & $ 24 \pm 1 $ & $ 1.53539 $ & $ 2.2522 $ & $ 0.000 \pm 0.000 $ \\ \hline
M79 & 0.0275 & 0.6 & $ 38 \pm 2 $ & $ 23 \pm 1 $ & $ 1.64486 $ & $ 2.41277 $ & $ 0.000 \pm 0.000 $ \\ \hline
M80 & 0.03 & 0.6 & $ 36 \pm 2 $ & $ 21 \pm 1 $ & $ 1.74271 $ & $ 2.55628 $ & $ 0.000 \pm 0.000 $ \\ \hline
